Estimating duration in the presence of misclassification

### 2024-03-25 introduction.tex
Proof ch 3

COVID-19 (coronavirus disease 2019), the disease caused by the virus SARS-CoV-2 (severe acute respiratory syndrome coronavirus 2), is estimated to have killed approximately 15 million in the most acute phase (to the end of 2021) and 30 million in total~\autocite{whoCOVIDExcess,economistCOVIDExcess}.

@@

The \emph{effective reproduction number}, $\Re$, is the mean number of secondary infections generated by a single infection at time $t$.
In particular, it uses the behaviour and immunity status of the population at time $t$.
With constant behaviour and a disease that grants immunity following infection, $\Re$ declines smoothly.
$\Re$ describes the current dynamics of the epidemic: $\Re > 1$ means the epidemic is growing, $\Re < 1$ means it is shrinking, and $\Re = 1$ means it is stable.
In simple epidemic models (see \cref{E-SEIR:sec:SIR}), $\Re$ is proportional to the product of the rate of contacts, the riskiness of those contacts, and the proportion of the population that is susceptible.
Therefore, it informs the strength of intervention, \eg social distancing or vaccination, required to control the epidemic.

The \emph{control reproduction number}, $\Rc$, is the mean number of secondary infections generated by a single infection with the behaviour at time $t$ but in a fully susceptible population.
$\Rc$ is also known as the \emph{reproduction number excluding immunity}.
It describes the effect on the epidemic of interventions (except vaccination) that are in place at time $t$.
$\Rc$ is useful when comparing the effects of interventions at different points in time, when the immunity status of the population has changed.
For example, when comparing the English lockdown in March 2020 and January 2021, there are two effects in play: there are more individuals with immunity in January 2021, and the lockdowns had different measures in place.
$\Rc$ focuses on the latter effect.

@@

Reproduction numbers are strongly connected to \emph{growth rates}.
Over short periods of time, epidemics tend to grow (or shrink) exponentially, and hence have an exponential growth rate, normally denoted $r$.
For a given disease and population, an analogous growth rate can be defined for each definition of the reproduction number~\autocite{pellisEstimation,paragGrowthRates,wallingaGI}.
The advantages of using the growth rates are that they are easier to estimate and capture how quickly spread happens in calendar time; however, they do not directly give the strength of intervention required to control the epidemic~\autocite{royalSocietyRnumber}.

@@

\emph{Prevalence} is the proportion of the population with the disease at a given time.
Whether a given individual is \emph{prevalent} (has the disease) is often measurable through diagnostic testing.
Therefore, the prevalence of the population can be estimated with a prevalence survey, although these are typically very expensive to power appropriately.
Prevalence and incidence are strongly related, via the duration of an infection (see \cref{E-inc-prev}).

@@

Data sources used for outbreak surveillance are often observational in nature.
Therefore, they suffer from biases that can be hard to understand and quantify~\autocite{shadboltChallenges}.
Here I discuss three types of data which are useful for surveillance: incidence-type, prevalence-type, and data from cohort studies.
\emph{Incidence-type} and \emph{prevalence-type} data can inform estimation of incidence and transmission; however, this estimation almost always relies on prior knowledge of epidemiological and/or biological quantities.
For example, the time between infection and symptom onset.
These quantities can be estimated from other studies, \eg cohort studies.

@@

An example of incidence-type data are community testing.
This relies on individuals presenting for a test, hence is biased by individuals' ability and willingness to be tested.

@@

Prevalence-type data originate from observations of the number or proportion of a population in a specific disease state at a specific time.
For example, the number of hospital beds occupied by individuals with the disease or the proportion of the population with a marker of prior infection.
The issues associated with incidence-type data often also apply to prevalence-type data.

@@

Other epidemiological and/or biological quantities are normally required to estimate transmission.
These depend on the model type, often including the duration of different disease stages or the distribution of the time between infection events~\autocite{wallingaGI,dankwaStructural}.
Cohort studies (following a group of individuals over time), are a study design which can estimate many of these quantities.

@@

At the core of many observation models is a \emph{convolution equation} or an approximation of it~\autocite[e.g.][]{brookmeyerBackcalculation,abbottEstimating,birrellRealtimea}.
This equation describes the expectation of $W_t$, conditional on the incidence prior to time $t$.
In discrete time, it is:
\begin{align}
    \E(W_t \mid Z_1, Z_2, \dots) &= \zeta \sum_{i=0}^\infty Z_{t-i} f(i)
    \label{intro:eq:disease-model}
\end{align}
where $Z_t$ is the incidence at time $t$; $\zeta$ is the proportion of infections that ever appear in $W_t$; and $f(i)$ is the probability that an infection at time $t-i$ is included in count $W_t$, conditional on it ever being in one of the counts.
$f$ is known as a \emph{delay function}.
$f$ is commonly the pdf of a distribution, or a transformation of it.

@@

Biases can arise in a variety of ways, \eg healthcare-seeking behaviour or tests which are less than 100\% accurate.
Bias can be modelled through additional parameters or data quantifying these issues~\autocite[e.g.][]{sherrattExploring,birrellRealtimea,nicholsonImproving,swallow2022challenges}.

Noise could come from a variety of sources, \eg sampling error, clustering, or unexplained overdispersion.
Noise is typically modelled by a parametric distribution \eg the negative binomial distribution allowing for overdispersion compared to a Poisson process assumption~\autocite[e.g.][]{birrellRealtimea,frassoBayesian}.

@@

The main data sources informing the response to the SARS-Cov-2 epidemic in England were: community testing (known as pillar 2 testing), the number of severe events, seroprevalence surveys, and prevalence surveys.
Each of these data sources have strengths and weaknesses, see \textcite{royalSocietyRnumber} and references therein for further details on each of these data sources.

@@

Severe events counts are generally a more reliable measure of the burden of the disease.
The criteria for being a severe event are normally well-defined and generally well-recorded in the UK context.
Therefore, these data are subject to fewer biases than community testing.
However, SARS-CoV-2 rarely leads to severe events in younger individuals, meaning severe event counts are insensitive to changes in transmission only occurring in younger individuals.

@@

Seroprevalence surveys were conducted throughout the epidemic, primarily in blood donors.
In addition to the normal problem of the delay between infection and antibody response, blood donors are a convenience sample whose representativeness of the wider population is unclear.

@@

A major advantage of the CIS over REACT is that the CIS has daily testing of individuals, while REACT has no test results between rounds.
This means that REACT cannot be used to estimate transmission or incidence between rounds, instead relying on model assumptions at these times.
A particular instance of this is that a peak in late December 2020 occurred between rounds of the REACT survey, complicating analysis of the survey data at that time~\autocite{rileyREACTround8}.

@@

In the UK, SPI-M-O (the Scientific Pandemic Influenza Group on Modelling, Operational sub-group) produced the most prominent modelling.
SPI-M-O was a sub-committee of SAGE (the Scientific Advisory Group for Emergencies), generating evidence based on infectious disease modelling for policy development~\autocite{medleySPIM,govSPIMO}.
This used a wide range of  modelling approaches depending on the data available, which fluctuated throughout the epidemic, and the question being addressed.
Some were fit to data while others were purely used for simulation based on plausible parameter values.

Each week, the members of SPI-M-O would produce a set of estimates of the current state of the epidemic (\eg the value of $\Re$), known as \emph{nowcasting}.
The committee reviewed these estimates, removing any estimates unduly affected by issues (e.g.. data quality issues), and then formed a consensus value using a statistical combination of the estimates~\autocite{parkCombining}.
The consensus value was published on the UK Government's website and informed its response to the epidemic~\autocite{govRnumber}.

@@

Some of these models were used to explore policy scenarios.
For example, the decision at each of stage of lifting the lockdown in 2021 was informed by modelling studies~\autocite{sageEvidence}.
These aided decision-makers in understanding plausible impacts of their actions.

@@

In this thesis, I consider how prevalence surveys could be used for epidemic surveillance.
These surveys have well-understood designs which means that estimates derived from them are more robust.
A crucial quantity in their use will be the distribution of the duration of RT-PCR positivity.

There is a large amount of related work in this area, from both prior to the pandemic and during its course.

@@

\emph{Backcalculation} is a modelling framework developed in the context of HIV/AIDS~\autocite{brookmeyerMethod} but applied very broadly.
It specifies a particular combination of infection, disease, and observation model to relate times of HIV infection with times of AIDS diagnosis via the incubation period.
Further details are in the recent review \textcite{sunModeling}.
The theory behind the framework underpins much of the work in this thesis.

The original formulation used a Poisson process as the infection model; a disease model where all infections are eventually observed ($\zeta = 1$) and the delay function, $f$, is the incubation period distribution's pdf; and an observation model where all diagnoses are observed, and hence has no influence on the data.

The disease and observation models must be adapted to apply backcalculation to SARS-CoV-2 prevalence surveys (elaborated on in \cref{E-inc-prev}).
The disease model must consider that this is now prevalence-type, rather than incidence-type data.
This difference induces a dependency structure between the observations on each day.
The observation model must consider that this is now a survey, with sampling error.

@@

\Textcite{hellewellPCRSensitivity} estimated the probability of an individual testing positive each day after infection.
This measure is highly related to the duration of positivity.
The study's cohort consisted of healthcare workers, \ie working-age adults.

>>>>

COVID-19, the disease caused by the virus SARS-CoV-2, is estimated to have killed approximately 15 million in the most acute phase (to the end of 2021) and 30 million in total~\autocite{whoCOVIDExcess,economistCOVIDExcess}.
Beyond the lives lost, there were massive health, economic, and societal costs.

@@

The \emph{effective reproduction number}, $\Re$, is the mean number of secondary infections generated by a single infection at time $t$.
In particular, it uses the behaviour and immunity status of the population at time $t$.
With constant behaviour and a disease that grants immunity following infection, $\Re$ declines smoothly.
$\Re$ describes the current dynamics of the epidemic: $\Re > 1$ means the epidemic is growing, $\Re < 1$ means it is shrinking, and $\Re = 1$ means it is stable.
In simple epidemic models (see \cref{E-SEIR:sec:SIR}), $\Re$ is proportional to the product of the rate of contacts, the probability of transmission upon contact, and the proportion of the population that is susceptible.
Interventions act by reducing one of these components \eg masks reduce the probability of transmission and vaccination reduce the susceptible population.
Therefore, $\Re$ informs the strength of intervention required to control the epidemic.

The \emph{control reproduction number}, $\Rc$, is the mean number of secondary infections that would be generated by a single infection at time $t$ if in a fully susceptible population.
$\Rc$ is also known as the \emph{reproduction number excluding immunity}.
It describes the effect on the epidemic of interventions (except vaccination) that are in place at time $t$.
$\Rc$ is useful when comparing the effects of interventions at different points in time, when the immunity status of the population has changed.
For example, when comparing the English lockdown in March 2020 and January 2021, there are two effects in play: there are more individuals with immunity in January 2021, and the lockdowns had different measures in place.
$\Rc$ quantifies the latter effect.

@@

Reproduction numbers are strongly connected to \emph{growth rates}.
If changes in behaviour and susceptibility are negligible, as they often are over short periods of time, epidemics grow (or shrink) exponentially.
The rate of this exponential growth is its \emph{growth rate}, normally denoted $r$.
For a given disease and population, an analogous growth rate can be defined for each definition of the reproduction number~\autocite{pellisEstimation,paragGrowthRates,wallingaGI}.
The advantages of using the growth rates are that they are easier to estimate and capture how quickly spread happens in calendar time; however, they do not directly give the strength of intervention required to control the epidemic~\autocite{royalSocietyRnumber}.

@@

\emph{Prevalence} is the proportion of the population with the disease at a given time.
Whether a given individual is \emph{prevalent} (has the disease) is often measurable through diagnostic testing.
Performing diagnostic tests in a sample of the population at a given point in time is known as a \emph{prevalence survey}.
Prevalence surveys can estimate the population prevalence but are typically very expensive to power appropriately.
Prevalence and incidence are strongly related, via the duration of an infection (see \cref{E-inc-prev}).

@@

Data sources used for outbreak surveillance are often observational in nature.
Therefore, they suffer from biases that can be hard to understand and quantify~\autocite{shadboltChallenges}.
These biases need to be accounted for when analysing the data.

Here I discuss three types of data which are useful for surveillance: incidence-type, prevalence-type, and data from cohort studies.
\emph{Incidence-type} and \emph{prevalence-type} data can inform estimation of incidence and transmission; however, this estimation almost always relies on prior knowledge of epidemiological and/or biological quantities.
For example, the time between infection and symptom onset.
These quantities can be estimated from other studies, \eg cohort studies.

@@

An example of incidence-type data are community testing, reliant on individuals presenting for a test.
However, individuals' ability and willingness to be tested varies over time, which needs to be accounted for in order to perform unbiased inference.
Unfortunately, data to estimate these changes is normally unavailable.

@@

Prevalence-type data originate from observations of the number or proportion of a population in a specific \emph{disease state} at a specific time.
Commonly used disease states are the presence or value of a biomarker or symptoms.
For example, the number of hospital beds occupied by individuals with the disease or the proportion of the population with a marker of prior infection.
The issues associated with incidence-type data often also apply to prevalence-type data.

@@

Other epidemiological and/or biological quantities are normally required to estimate transmission.
These depend on the model type, often including the duration of different disease states or the distribution of the time between infection events~\autocite{wallingaGI,dankwaStructural}.
Cohort studies (following a group of individuals over time), are a study design which can estimate many of these quantities.

@@

At the core of many observation models is a \emph{convolution equation} or an approximation of it~\autocite[e.g.][]{brookmeyerBackcalculation,abbottEstimating,birrellBayesian}.
This equation describes the expectation of $W_t$, conditional on the incidence prior to time $t$.
In discrete time, it is:
\begin{align}
    \E(W_t \mid Z_1, Z_2, \dots) &= \zeta \sum_{i=0}^\infty Z_{t-i} f(i)
    \label{intro:eq:disease-model}
\end{align}
where $Z_t$ is the incidence at time $t$; $\zeta$ is the proportion of infections that ever appear in $W_t$; and $f(i)$ is the probability that an infection at time $t-i$ is included in count $W_t$, conditional on it ever being in one of the counts.
$f$ is known as a \emph{delay function}.
$f$ is commonly the pdf of a distribution, or a transformation of it.

@@

Biases can arise in a variety of ways, \eg healthcare-seeking behaviour or tests which are less than 100\% accurate.
Bias can be modelled through additional parameters or data quantifying these issues~\autocite[e.g.][]{sherrattExploring,birrellBayesian,nicholsonImproving,swallow2022challenges}.

Noise could come from a variety of sources, \eg sampling error, clustering, or unexplained overdispersion.
Noise is typically modelled by a parametric distribution \eg the negative binomial distribution allowing for overdispersion compared to a Poisson process assumption~\autocite[e.g.][]{birrellBayesian,frassoBayesian}.

@@

The main data sources informing the response to the SARS-Cov-2 epidemic in England were based on: community testing (known as pillar 2 testing), the number of severe events, seroprevalence surveys, and prevalence surveys.
Each of these data sources have strengths and weaknesses, see \textcite{royalSocietyRnumber} and references therein for further details on each of these data sources.

@@

Severe events counts are generally a more reliable measure of the burden of the disease.
The criteria for being a severe event are normally well-defined and generally well-recorded in the UK context.
Therefore, these data are subject to fewer biases than community testing.
However, SARS-CoV-2 rarely leads to severe events in younger individuals, meaning severe event counts are insensitive to changes in transmission only affecting younger individuals.

@@

Seroprevalence surveys were conducted throughout the epidemic, the largest of which was tested donated blood~\autocite{amirthalingamSeroprevalence}.
In addition to the normal problem of the delay between infection and antibody response, blood donors are a convenience sample whose representativeness of the wider population is unclear.

@@

A major advantage of the CIS over REACT is that the CIS had continual data collection, while REACT has no test results between rounds.
The lack of data between rounds meant that using REACT data to infer transmission in these periods requires strong model assumptions.
A particular instance of this is that a peak in late December 2020 occurred between rounds of the REACT survey, complicating analysis of the survey data at that time~\autocite{rileyREACTround8}.

@@

Members of SPI-M-O (the Scientific Pandemic Influenza Group on Modelling, Operational sub-group) produced the most prominent modelling of the UK epidemic.
SPI-M-O was a sub-committee of SAGE (the Scientific Advisory Group for Emergencies), generating evidence based on infectious disease modelling for policy development~\autocite{medleySPIM,govSPIMO}.
This used a wide range of  modelling approaches depending on the data available, which fluctuated throughout the epidemic, and the question being addressed.
Some were fit to data while others were purely used for simulation based on plausible parameter values.

Each week, members of SPI-M-O would produce a set of estimates of the current state of the epidemic (\eg the value of $\Re$), known as \emph{nowcasting}.
The committee peer-reviewed these estimates to provide quality assurance, removing any estimates unduly affected by issues (\eg data quality issues).
They then formed a consensus value using a statistical combination of the estimates~\autocite{parkCombining}.
The consensus value was published on the UK Government's website and informed its response to the epidemic~\autocite{govRnumber}.

@@

Additionally, these models were used to explore policy scenarios.
For example, the decision at each of stage of lifting the lockdown in 2021 was informed by modelling studies~\autocite{sageEvidence}.
These aided decision-makers in understanding plausible impacts of their actions.

@@

In this thesis, I consider how prevalence surveys could be used for epidemic surveillance, in particular estimates of incidence and transmission.
These surveys have well-understood designs which means that estimates derived from them are more robust.
A crucial quantity in their use will be the distribution of the duration of RT-PCR positivity.

In the following subsection, I introduce the most relevant related work, from both prior to the pandemic and during its course.

@@

\emph{Backcalculation} is a modelling framework developed in the context of HIV/AIDS~\autocite{brookmeyerMethod} but applied very broadly.
It specifies a particular combination of infection, disease, and observation model which relate times of HIV infection with times of AIDS diagnosis via the incubation period.
Further details are in the recent review \textcite{sunModeling}.
The theory behind the framework underpins much of the work in this thesis.

The original formulations~\autocite{brookmeyerMethod,rosenbergBackcalculation} used a Poisson process as the infection model; a disease model where all infections are eventually observed ($\zeta = 1$) and the delay function, $f$, is the incubation period distribution's pdf; and an observation model where all diagnoses are observed, and hence has no influence on the data.

The disease and observation models must be adapted to apply backcalculation to SARS-CoV-2 prevalence surveys (see \cref{E-inc-prev}).
The disease model must consider that this is now prevalence-type, rather than incidence-type data.
This difference induces a dependency structure between the observations on each day.
The observation model must now include the with error arising from using a sample of the population rather than (assumed) full recording of AIDS diagnoses.

@@

\Textcite{hellewellPCRSensitivity} estimated the probability of an individual testing positive each day after infection.
This measure is highly related to the duration of positivity.
However, the study's cohort consisted only of healthcare workers, \ie working-age adults.

### 2024-03-25 transmission.tex
plural data
proof
Proof ch 3

In this chapter, I use the estimate of the duration of RT-PCR positivity from combining information from the ATACCC and CIS studies (see \cref{E-imperf-test:sec:conclusion}) to investigate the feasibility of estimating incidence and transmission of SARS-CoV-2 from only the CIS data (described in \cref{E-intro:sec:cis}).
I will show that the CIS data is sufficient, demonstrating the value of surveys of this type for pandemic surveillance.

@@

% First, I draw a sample of 500 prevalence time series in each stratum from the approximate posterior distribution (using the procedure described in \cref{transmission:sec:INLA:posterior}).
% For each sample and stratum, I use the relationship in \cref{E-inc-prev:eq:EPt} to calculate the incidence proportion at each time point.
% I consider the relationship between incidence and prevalence within a stratum to be deterministic, as \cref{E-inc-prev:sec:observation-process} justifies, that is the estimate of the incidence is negligibly affected by approximating the distribution $\vec{P} \mid \vec{Z}$ by its mean.
% I solve this system using forward substitution, calculating the value of $Z_t$ in \cref{inc-prev:eq:forward-substitute} sequentially for $t = 1, \dots, T$.
% $t = 1$ is defined as the first day where prevalence data is used.
% \Cref{inc-prev:eq:forward-substitute} is repeated here for convenience:
% \begin{align}
% Z_t
% &= \frac{P_t - \sum_{i=1}^{t-1} S_{ti} Z_i}{S_{tt}} \\
% &= P_t - \sum_{i=1}^{t-1} S(t - i + 1) Z_i.
% \label{transmission:eq:forward-substitute}
% \end{align}
% % \Cref{E-inc-prev:eq:EPt}, considered across different values of $t$, can be written as $\vec{P} = \matr{S} \vec{Z}$, where: $\vec{P}$ is a vector of the number of prevalent individuals at each time point in the stratum; $\matr{S}$ is a matrix formed from the survival function, as defined below; and $\vec{Z}$ is a vector of the incidence at each time point in the stratum.
% Dividing each side by the total number of individuals in each stratum transforms the number of prevalent individuals to prevalence and incidence to incidence proportion.

@@

I model each region fully independently, \ie with no shared parameters or transmission between regions.
As well as the motivation given in \cref{E-backcalc}, independent regions allow heterogeneity in the parameters between regions, which could arise from a range of socioeconomic factors.
Furthermore, the assumption of homogeneous mixing within age groups is more plausible for regions than the whole of England.
By modelling each region independently, I assume that the epidemics in each region do not interact.
Clearly, this is not realistic as travel between regions of England is common and unrestricted.
However, except in an epidemic's early stages, the interaction between large regions has a negligible impact on the epidemic's progression~\autocite[e.g.][]{birrellRealtimea,gogSpatial,eggoSpatial}.

@@

% $K_{ij}$ and $\beta_{ij}$ appear only as a product and therefore are not individually identifiable.
% Normally, $K_{ij}$ is assumed to be known, for example from a previous contact survey~\autocite[such as][]{mossongSocial}.
% Ideally, all the $\beta_{ij}$ terms would be estimated, but there is normally inadequate data to do so, requiring assumptions to be made to reduce the number of parameters~\autocite[65]{keelingModeling}.
% % $\beta_{ij}$ is then estimated, although often with a parsimonious model
% A common assumption is that $\beta_{ij}$ can be decomposed into two independent components such that $\beta_{ij} = \beta \beta^\text{susc}_{i} \beta^\text{inf}_j$.
% For any stratum $i$, $\beta^\text{susc}_i$ is known as the \emph{relative susceptibility} of stratum $i$.

@@

I solve the system of ODEs using Euler's method, discretised at timesteps of $\delta t = 1/2$ days.
That is, if $\vec{x}_t$ is the system state at time $t$ for $t \in \{ 0, 0.5, 1, \dots \}$ then $x_{t+\frac{1}{2}} = x_t + (d\vec{x}(t)/dt) \delta t$.

>>>>

In this chapter, I use the estimate of the duration of RT-PCR positivity from combining information from the ATACCC and CIS studies (see \cref{E-imperf-test:sec:conclusion}) to investigate the feasibility of estimating incidence and transmission of SARS-CoV-2 from only the CIS data (described in \cref{E-intro:sec:cis}).
I will show that the CIS data are sufficient, demonstrating the value of surveys of this type for pandemic surveillance.

@@

% First, I draw a sample of 500 prevalence time series in each stratum from the approximate posterior distribution (using the procedure described in \cref{transmission:sec:INLA:posterior}).
% For each sample and stratum, I use the relationship in \cref{E-inc-prev:eq:EPt} to calculate the incidence proportion at each time point.
% I consider the relationship between incidence and prevalence within a stratum to be deterministic, as \cref{E-inc-prev:sec:observation-process} justifies, that is the estimate of the incidence is negligibly affected by approximating the distribution $\vec{P} \mid \vec{Z}$ by its mean.
% I solve this system using forward substitution, calculating the value of $Z_t$ in \cref{inc-prev:eq:forward-substitute} sequentially for $t = 1, \dots, T$.
% $t = 1$ is defined as the first day where prevalence data are used.
% \Cref{inc-prev:eq:forward-substitute} is repeated here for convenience:
% \begin{align}
% Z_t
% &= \frac{P_t - \sum_{i=1}^{t-1} S_{ti} Z_i}{S_{tt}} \\
% &= P_t - \sum_{i=1}^{t-1} S(t - i + 1) Z_i.
% \label{transmission:eq:forward-substitute}
% \end{align}
% % \Cref{E-inc-prev:eq:EPt}, considered across different values of $t$, can be written as $\vec{P} = \matr{S} \vec{Z}$, where: $\vec{P}$ is a vector of the number of prevalent individuals at each time point in the stratum; $\matr{S}$ is a matrix formed from the survival function, as defined below; and $\vec{Z}$ is a vector of the incidence at each time point in the stratum.
% Dividing each side by the total number of individuals in each stratum transforms the number of prevalent individuals to prevalence and incidence to incidence proportion.

@@

I model each region fully independently, \ie with no shared parameters or transmission between regions.
As well as the motivation given in \cref{E-backcalc}, independent regions allow heterogeneity in the parameters between regions, which could arise from a range of socioeconomic factors.
Furthermore, the assumption of homogeneous mixing within age groups is more plausible for regions than the whole of England.
By modelling each region independently, I assume that the epidemics in each region do not interact.
Clearly, this is not realistic as travel between regions of England is common and unrestricted.
However, except in an epidemic's early stages, the interaction between large regions has a negligible impact on the epidemic's progression~\autocite[e.g.][]{birrellBayesian,gogSpatial,eggoSpatial}.

@@

% $K_{ij}$ and $\beta_{ij}$ appear only as a product and therefore are not individually identifiable.
% Normally, $K_{ij}$ is assumed to be known, for example from a previous contact survey~\autocite[such as][]{mossongSocial}.
% Ideally, all the $\beta_{ij}$ terms would be estimated, but there is normally inadequate data to do so, requiring assumptions to be made to reduce the number of parameters~\autocite[65]{keelingModeling}.
% % $\beta_{ij}$ is then estimated, although often with a parsimonious model.
% A common assumption is that $\beta_{ij}$ can be decomposed into two independent components such that $\beta_{ij} = \beta \beta^\text{susc}_{i} \beta^\text{inf}_j$.
% For any stratum $i$, $\beta^\text{susc}_i$ is known as the \emph{relative susceptibility} of stratum $i$.

@@

I solve the system of ODEs using Euler's method, discretised at timesteps of $\delta t = 1/2$ days.
That is, if $\vec{x}_t$ is the system state at time $t$ for $t \in \{ 0, 0.5, 1, \dots \}$ then $y_{t+\frac{1}{2}} = y_t + (d\vec{x}(t)/dt) \delta t$.
